Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-09-24 paper/paper.tex
added hemagglutination details

We generated the wildtype and point-mutant viruses for the validation experiments in \FIG{validation}A by reverse genetics using the pHW18* series of WSN reverse genetics plasmids~\citep{hoffmann2000dna}, but substituting the appropriate mutant plasmid listed in \FIGDATA[validation]{sequences} for the wildtype plasmid for that gene.
To generate the viruses from these plasmids, we transfected an equimolar mix of all eight plasmids into co-cultures of 293T and MDCK-SIAT1 cells seeded at a ratio of 8:1.
At 24 hours post-transfection, we changed media from D10 to influenza growth media. 
At 50 hours post-transfection (for the replicate 1 viruses in \FIGSUPP[validation]{SNPflow}) or 72 hours (for the replicate 2 viruses in \FIGSUPP[validation]{SNPflow}), we harvested the virus-containing supernatant, clarified this supernatant by centrifugation at 300$\times$g for 4 min, and stored aliquots of the clarified viral supernatant at -80$^{\circ}$C.
We then thawed aliquots and titered by TCID50 on MDCK-SIAT1 cells.
For the infections in \FIGSUPP[validation]{SNPflow}, we wanted to use equivalent particle counts, so we normalized all viruses to an equivalent HI titer on \jdbcomment{red blood cells from what species where, and is there citation to protocol?}.
We then performed infections of the A549 reporter cell line at equivalent HI titer and analyzed the data as described in \FIGSUPP[validation]{SNPflow}.

>>>>

We generated the wildtype and point-mutant viruses for the validation experiments in \FIG{validation}A by reverse genetics using the pHW18* series of WSN reverse genetics plasmids~\citep{hoffmann2000dna}, but substituting the appropriate mutant plasmid listed in \FIGDATA[validation]{sequences} for the wildtype plasmid for that gene.
To generate the viruses from these plasmids, we transfected an equimolar mix of all eight plasmids into co-cultures of 293T and MDCK-SIAT1 cells seeded at a ratio of 8:1.
At 24 hours post-transfection, we changed media from D10 to influenza growth media. 
At 50 hours post-transfection (for the replicate 1 viruses in \FIGSUPP[validation]{SNPflow}) or 72 hours (for the replicate 2 viruses in \FIGSUPP[validation]{SNPflow}), we harvested the virus-containing supernatant, clarified this supernatant by centrifugation at 300$\times$g for 4 min, and stored aliquots of the clarified viral supernatant at -80$^{\circ}$C.
We then thawed aliquots and titered by TCID50 on MDCK-SIAT1 cells.
For the infections in \FIGSUPP[validation]{SNPflow}, we wanted to use equivalent particle counts, so we normalized all viruses to an equivalent hemagglutination titer on turkey red blood cells ~\citep{hirs1941tHI}.
 Briefly, a solution of 10\% v/v red blood cells was washed in PBS and diluted to a final concentration of 0.5\% v/v. 
Two-fold serial dilutions of virus were added to an equal volume of diluted red blood cells, and titer was measured as the highest dilution of viral stock at which complete hemagglutination of red blood cells was observed.
We then performed infections of the A549 reporter cell line at equivalent hemagglutination titer and analyzed the data as described in \FIGSUPP[validation]{SNPflow}.
